Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-07 journal paper/content/sec-intro.tex
Moved/reworded the note re discrepancy on HardMax.

\begin{itemize}
\item We compare \HardMax and \HardMaxRandom decision rules. We find that the greedy algorithm often wins under \HardMax, with a strong evidence of the ``death spiral" effect mentioned earlier.%
\footnote{The greedy algorithm wins often but not always, whereas it
always wins under \TheoryModel. The reason for this discrepancy is that the greedy algorithm in the theoretical results is aware of the Bayesian prior.
}
 As predicted by the theory, better algorithms prevail if the expected number of ``random" users is sufficiently large. However, this effect is negligible for smaller parameter values.

@@

\item We investigate the algorithms' performance ``in isolation", \ie without competition. We suggest a new performance measure to explain why the greedy algorithm is sometimes not the best strategy under high levels of competition. We find that mean reputation -- arguably, the most natural performance measure ``in isolation" -- is sometimes \emph{not} a good predictor for the outcomes under competition.

>>>>

\begin{itemize}
\item We compare \HardMax and \HardMaxRandom decision rules. We find that the greedy algorithm often wins under \HardMax, with a strong evidence of the ``death spiral" effect mentioned earlier. 
 As predicted by the theory, better algorithms prevail if the expected number of ``random" users is sufficiently large. However, this effect is negligible for smaller parameter values.

@@

\item We investigate the algorithms' performance ``in isolation", \ie without competition. We suggest a new performance measure to explain why the greedy algorithm is sometimes not the best strategy under high levels of competition.%
    \footnote{Note the discrepancy with our theoretical results on \HardMax: there, the greedy algorithm is always the best strategy, mainly because it is aware of the Bayesian prior (whereas in the simulations the prior is not available).}
     We find that mean reputation -- arguably, the most natural performance measure ``in isolation" -- is sometimes \emph{not} a good predictor for the outcomes under competition.
